### 2022-05-06 manuscript.Rmd

+-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
| Available statistics                                                  | Conversion to standardized mean difference (Hedges' $g$)                             |
+=======================================================================+======================================================================================+
| (1) Cohen's $d$ and sample size $n$                                   | $df=2(n-1)$;\quad                                                                    |
| [@goulet-pelletier2018; @hedges1985]                                  | $j=\frac{\Gamma(\frac{1}{2}df)}{\sqrt{\frac{df}{2}}\Gamma(\frac{1}{2}(df-1))}$;\quad |
|                                                                       | $g=d*j$                                                                              |
+-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
| (2) $t$-statistic and sample size $n$                                 | $d=\frac{t}{\sqrt{n}}$;\quad                                                         |
| [@rosenthal1991]                                                      | then (1)                                                                             |
+-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
| (3) Mean difference $m_\text{diff}$ and $SD_\text{diff}$              | $d=\frac{m_\text{diff}}{SD_\text{diff}}$;\quad                                       |
| [@lakens2013]                                                         | then (1)                                                                             |
+-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
| (4) Mean looking times per condition + $SD$s                          | $SD_\text{av}=\sqrt{\frac{SD_\text{novel}^2+SD_\text{familiar}^2}{2}}$;\quad         |
| [@cumming2012]                                                        | $d=\frac{m_\text{movel}-m_\text{familiar}}{SD_\text{av}}$;\quad                      |
|                                                                       | then (1)                                                                             |
+-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
| (5) Mean novelty preference score $m_\text{pref}$ + $SD_\text{pref}$  | $d=\frac{m_\text{pref}}{SD_\text{pref}}$;\quad                                       |
| [@lakens2013]                                                         | then (1)                                                                             |
+-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+

>>>>

+-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
| Available statistics                                                  | Conversion to standardized mean difference (Hedges' $g$)                             |
+=======================================================================+======================================================================================+
| (1) Cohen's $d$ and group sample size $n$                             | $df=n_{female}+ n_{male}-1$; \quad                                                   |
| [@goulet-pelletier2018; @hedges1985]                                  | $j=\frac{\Gamma(\frac{1}{2}df)}{\sqrt{\frac{df}{2}}\Gamma(\frac{1}{2}(df-1))}$;\quad |
|                                                                       | $g=d*j$                                                                              |
+-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
| (2) $t$-statistic and group sample size $n$                           | $d = t \sqrt{\frac{1}{n_{female}} + \frac{1}{n_{male}$;\quad                         |
| [@lankens2013]                                                        | then (1)                                                                             |
+-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
| (3) $F$ statistic and group sample size                               | $d = \sqrt{f} \sqrt{\frac{1}{n_{female}} + \frac{1}{n_{male}$;\quad                  |
| [@lakens2013]                                                         | then (1)                                                                             |
+-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
| (4) Mean difference in looking times per group + $SD$s                | $SD_\text{mean} = \sqrt{\frac{{(n_{female} - 1) \sigma^2_{female} + (n_{male} -1) \sigma^2_{male}}}{df}}$;\quad |
| [@lankens2013]                                                        | $d=\frac{m_\text{female}-m_\text{male}}{SD_\text{mean}}$;\quad                       |
|                                                                       | then (1)                                                                             |
+-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
| (5) Mean novelty preference score $m_\text{pref}$ + $SD_\text{pref}$  | $SD_\text{pref} = \sqrt{\frac{{(n_{female} - 1) \sigma^2_{female} + (n_{male} -1) \sigma^2_{male}}}{df}}$;\quad |
|  [@lakens2013]                                                        | $d=\frac{m_\text{female}-m_\text{male}}{SD_\text{pref}}$;\quad                       |
|                                                                       | then (1)                                                                             |
+-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
